### 2016-10-25 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
Edits

temp <- subset(dd,LayYear>1995)
temp$JA <- ifelse(temp$Ageclass == 'A','Adults','Juveniles')

Fig2 <- ggplot(temp,aes(x = LayYear,y = RTL))+
  ylab('RTL') + 
  xlab('Cohort') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12,angle = 90), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'top')+
  geom_boxplot(aes(group = LayYear),outlier.colour = 'grey',notch=F,alpha=0)+
  geom_smooth()

pdf('Figures/Figure 2.pdf',
    width = 8,
    height = 4,
    paper = 'a4r')
Fig2
dev.off()

>>>>

ys <- names(which(table(subset(dd,Ageclass == 'CH')$LayYear)>10))
temp <- subset(dd,LayYear %in% ys)
temp$Cohort <- factor(temp$LayYear)

Fig2A <- ggplot(temp,aes(x = Agemonths,y = RTL,col = Cohort))+
  xlab('Age (months)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'))+
  geom_smooth(method = 'lm',formula = y~log(x),se = F)+
  annotate('text',x = 0,y = 1.3,label = 'A')

Fig2B <- ggplot(temp,aes(x = Agemonths,y = RTL,col = Cohort))+
  xlab('Age (months)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'))+
  geom_smooth(se = F)+
  annotate('text',x = 0,y = 1.4,label = 'B')

pdf('Figures/Figure 2.pdf',
    width = 5,
    height = 8,
    paper = 'a4')
multiplot(Fig2A,Fig2B)
dev.off()
